---
title: "ANA 510 Assignment 1"
author: alicia saputra
date: 2021
output: 
  html_document:
    theme: journal
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Installing the packages
```{r}
install.packages('tidyverse')
install.packages('knitr')
install.packages('bslib')
```
#Importing data from CSV
```{r}
url <- "https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv"
fivethiryeight <- read_csv(url)
glimpse(fivethiryeight)
```
#Calling my install packages
```{r}
library(tidyverse)
library(knitr)
library(bslib)
```
#create a new dataset named youth
```{r}
youth <- filter(fivethiryeight,age >=65)
```
#Summary of youth dataset
```{r}
summary (youth)
```
#Inline code
```{r,echo=false}
#This next chunk is my inline code
```
We have data about `r nrow(fivethiryeight)`individual killed by guns. 
Only `r nrow(fivethiryeight) - nrow(youth)` are older than 65. 
The distribution of the remainder is shown below:
#This next code chunk will graph the distribution of the age variable from the youth dataset
```{r youth-dist, echo = FALSE} 
youth %>% 
  ggplot(aes(age)) + 
  geom_freqpoly(binwidth = 1) 
```
#This next code chunk will graph the distribution by race
```{r race-dist, echo = FALSE} 
youth %>% 
  ggplot(aes(fct_infreq(race) %>% fct_rev())) + 
  geom_bar() + coord_flip() + 
  labs(x = "Victim race") 
```
